Prefetching SPARQL query cacher

### 2016-07-27 dissertation/cache-proxy.tex
triple store -> triplestore, thanks @kasei

The system is in the convergence of the directions described in this
thesis: It should relieve the remote endpoint of some of the
burden to evaluate the query and it should add to the robustness of
the open Web SPARQL infrastructure. It uses hypermedia to answer
individual triple patterns, based on Triple Pattern Fragments (TPF)
\cite{ldf1}. The system does not support named graphs (i.e. only
triple stores), but other than that, it supports SPARQL 1.1 in its
entirety. It was possible to develop this quickly by the efforts put
into the query planning in the Attean framework described in
Section~\ref{sec:conpush}. Caching based on RFC7234 \cite{rfc7234} was
shown to be of possible use in the survey I conducted. Finally, it was
planned to be evaluated using Design of Experiments.

@@

Stores can be rather diverse, so in addition, Attean provides another
abstraction layer, called a Model. Models consistently operate over
quads, in the case where underlying store is a triple store, a graph
name will be set, or it may wrap several triple stores with a graph
name for each. In addition, Models provide higher level methods,
for example a \pcode{subject} method to list all subjects, and
corresponding for other terms. Thus, upper layers of an application
should use the Model abstraction. We have also chosen to implement significant
parts of the query planning in the Model.

@@

The Linked Data Fragment client work was started prior to this project
by Patrick Hochstenbach, and consists of the client code for Triple
Pattern Fragments in \pmodule{RDF::LDF}. It also includes the Basic
Graph Pattern optimisation from \cite{verborgh2014querying}. Included with the client
code is an implementation of a triple store of the legacy
\pmodule{RDF::Trine} framework that predates Attean. He also started
an Attean store implementation \pmodule{AtteanX::Store::LDF} as a
separate module, but that module was subsequently adopted by me, and I
have written most of the functionality. It composes the TripleStore
and CostPlanner APIs and implements triple pattern queries and
cardinality estimates, both provided by the underlying client code as
they are a part of the core functionality of TPF,
as well as \pcode{cost\_for\_plan}.

>>>>

The system is in the convergence of the directions described in this
thesis: It should relieve the remote endpoint of some of the
burden to evaluate the query and it should add to the robustness of
the open Web SPARQL infrastructure. It uses hypermedia to answer
individual triple patterns, based on Triple Pattern Fragments (TPF)
\cite{ldf1}. The system does not support named graphs (i.e. only
triplestores), but other than that, it supports SPARQL 1.1 in its
entirety. It was possible to develop this quickly by the efforts put
into the query planning in the Attean framework described in
Section~\ref{sec:conpush}. Caching based on RFC7234 \cite{rfc7234} was
shown to be of possible use in the survey I conducted. Finally, it was
planned to be evaluated using Design of Experiments.

@@

Stores can be rather diverse, so in addition, Attean provides another
abstraction layer, called a Model. Models consistently operate over
quads, in the case where underlying store is a triplestore, a graph
name will be set, or it may wrap several triplestores with a graph
name for each. In addition, Models provide higher level methods,
for example a \pcode{subject} method to list all subjects, and
corresponding for other terms. Thus, upper layers of an application
should use the Model abstraction. We have also chosen to implement significant
parts of the query planning in the Model.

@@

The Linked Data Fragment client work was started prior to this project
by Patrick Hochstenbach, and consists of the client code for Triple
Pattern Fragments in \pmodule{RDF::LDF}. It also includes the Basic
Graph Pattern optimisation from \cite{verborgh2014querying}. Included with the client
code is an implementation of a triplestore of the legacy
\pmodule{RDF::Trine} framework that predates Attean. He also started
an Attean store implementation \pmodule{AtteanX::Store::LDF} as a
separate module, but that module was subsequently adopted by me, and I
have written most of the functionality. It composes the TripleStore
and CostPlanner APIs and implements triple pattern queries and
cardinality estimates, both provided by the underlying client code as
they are a part of the core functionality of TPF,
as well as \pcode{cost\_for\_plan}.
